---
title: "Statistical analysis of profile with CSProfile package"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    df_print: paged

vignette: |
  %\VignetteIndexEntry{CSProfile package}    %\VignetteEngine{knitr::rmarkdown}  \usepackage[utf8]{inputenc}
header-includes: \usepackage{amsfonts}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction
CSProfile aims to analyze data from different protocols of sensory analysis -especially providing from TimeSens software ,but not only-. 
This vignette is dedicated to sensory profiling. 


```{r, eval=TRUE,echo=TRUE,message=FALSE}
library(CSProfile)
```


# Reading a profile object

```{r, eval=TRUE,echo=TRUE,warning=FALSE,message=FALSE}
profileObject=profileReadData(file="../data/profile.csv",allData=NULL,
                              replaceNA="crossmean",sep=";",
                              transformSessionIntoReplicate=TRUE,
                              percentageOfSubjectsByReplicate=0,                               percentageOfReplicatesBySubject=0,percentageOfProductBySubject=0)
```

```{r, eval=TRUE,echo=TRUE,warning=FALSE}
names(profileObject)
```

# Descriptive analysis

## Table of statistics
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_stats=profileDescriptiveStatistics(profileObject,by="AttributeCode")
res_stats=profileDescriptiveStatistics(profileObject,by="ProductCode")
```

<!-- ```{r, echo=FALSE} -->
<!-- htmltools::includeHTML("DescriptiveStatistics.html") -->
<!-- ``` -->
## Boxplots
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_boxplot=profileBoxPlot(profileObject,variable="Butter")
```

## Barplots
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_barplot=profileBarPlot(profileObject,variable="Butter")
```

## Radarplot
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_radarplot=profileRadarPlot(profileObject)
```

# Product analysis

## ANOVA results
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_anova=profileAnova(profileObject,model="DefaultModel", randomEffects=c("Subject"), lsMeansAlpha=0.10, lsMeansAdjustment="Tukey", anovaCalculationMode="Ols", show=c("Groups","StatMANOVA","F", "PValues","RMSE"),fileName=NULL,varianceTest="None", normalityTest="None",orderByF=TRUE)
```

```{r, echo=FALSE}
htmltools::includeHTML("ANOVA of scores.html")
```

## Flash table
```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_flashtable=profileFlashTable(profileObject,classificationMethod="Complete", explainedVariance=0.5, alphaContrast=0.1, similarity="Pearson", fileName="FlashTable", show="",contrastOption="GMean",contrastProduct=NULL)
```

```{r, echo=FALSE}
htmltools::includeHTML("FlashTable.html")
```

## Use of MAM model 
```{r, eval=FALSE,echo=TRUE}
res_mam=profileMAM(profileObject)
```
```{r, echo=FALSE}
# htmltools::includeHTML("MAM.html")
```
# Panel and panellist performances

## MAMCAP Table

```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_mamcaptable=profileCAPTable(profileObject,model="MAM",output = "MAMCAPTable")
```

```{r, echo=FALSE}
htmltools::includeHTML("MAMCAPTable.html")
```

##CAP Table

```{r, eval=TRUE,echo=TRUE,warning=FALSE}
res_captable=profileCAPTable(profileObject,model="CAP")
```
```{r, echo=FALSE}
htmltools::includeHTML("CAPTable.html")
```
# Product mapping

## PCA

```{r, eval=TRUE,echo=TRUE}
res_pca=profilePCA(profileObject,itemsToPlot=c("ProductEllipses","Panellists"))

```

## CVA

```{r, eval=TRUE,echo=TRUE}
res_cva=profileCVA(profileObject,itemsToPlot=c("ProductEllipses","ProductSegments"))
```
